Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-12-08 02_Paper/paper.tex
Quality control in production

The quality characteristics of a product can be classified as variables or attributes.
Variables are measurable characteristics, which are shown as numbers. On the contrary, attributes are not measurable and can only take the binary values like "go" or "no-go" \cite{mitra2016fundamentals}. 
The advantage of variable measurements is that in the event of a defective intermediate or end product, precise measured values are available, which enable precise adjustment of the process parameters. 
This allows the desired quality to be restored. With that in mind, predictive quality control is a promising solution.

>>>>

The quality characteristics of a product can be classified as variables or attributes.
Attributes are qualitative measurable characteristics, i.e, color, texture, other. Variables are quantitative measurable characteristics, which are shown as numbers \cite{mitra2016fundamentals}. 
The advantage of variable measurements is that in the event of a defective intermediate or end product, precise measured values are available, which enable precise adjustment of the process parameters, as well as the the posibility of observing trends in the collected data. This would enable the possibility to employ predictive models to determine the quality of the product before the QC process takes place. With that in mind, predictive quality control is a promising solution.
